The Effect of Oil Price on Field Production: Evidence from the Norwegian Continental Shelf

### 2015-03-21 oil_prices_rr.tex
created appendix

\section{A generalized additive model of oil field production}
Parametric linear models have the sizeable advantages of simplicity and interpretability and are therefore usually a good starting point for an analysis.  However, when attempting to model the effect of price on oil field production, a standard linear model is unable to sufficiently control for the production profile and therefore heavily biases the estimate of the effect of price.  As an example, consider a generalized linear model written as in equation \ref{glm_eqn}.

>>>>

\section{A generalized additive model of oil field production}
Parametric linear models have the sizeable advantages of simplicity and interpretability and are therefore usually a good starting point for an analysis.However, when attempting to model the effect of price on oil field production, a standard linear model is unable to sufficiently control for the production profile and therefore heavily biases the estimate of the effect of price.  As an example, consider a generalized linear model written as in equation \ref{glm_eqn}.
